Towards Transparency and Open Science

### 2023-02-15 manuscript.Rmd
passive; also facilitate > help

Most readers will recognize that this information-theoretic setup and the derivation below follow closely @burnhamModelSelectionMultimodel2002, Ch. 7.2, in their derivation of the Akaike Information Criterion [@hirotuguakaikeInformationTheoryExtension1971] in its general form.
What is of interest is not the derivation but how this conceptualization may help us to understand what happens when data is simultaneously used to induce quantities of a theory and to test the theory.

>>>>

Most readers will recognize that this information-theoretic setup and the derivation below follow closely @burnhamModelSelectionMultimodel2002, Ch. 7.2, in their derivation of the Akaike Information Criterion [@hirotuguakaikeInformationTheoryExtension1971] in its general form.
What is of interest is not the derivation but how this conceptualization may facilitate to understand what happens when data is simultaneously used to induce quantities of a theory and to test the theory.
